Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2019-01-03 papers/paper/paper.tex
Remove unused references from paper.bib and add some more.

Dynein's mechanism of motion generation is the least understood of all motor proteins. Kinesin and myosin both take periodic, consistent steps of 8nm. In contrast, dynein is known to take highly variant steps both forwards and backwards, but averaging 16nm \cite{yildizpaper, weihongpaper}. Another interesting feature of dynein is the 20nm separation between its ATP hydrolysis and the site and MT binding site \cite{3vkh-cite}. The protein must transmit information about ATP binding across this distance in order to coordinate its steps \cite{mt-atp-coupling}. Explaining these phenomena is necessary to fully understand dynein's mechanism.\\

@@

\subsection*{Equilibrium forces}
The onebound model has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$. The bothbound model has two: $\theta_{nm}$ and $\theta_{fm}$. The model is free to vary across all of these degrees of freedom, barring steric interactions with the microtubule. These angles describe a planar model which is not capable of transverse motion. To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for onebound and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for bothbound. Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain. These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}. Electron microscopy studies using ADP-Vi to freeze dynein in the pre-powerstroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.\\

\subsection*{Brownian dynamics}
Brownian dynamics is used to study the model's dynamics in a biophysical manner. In the Brownian regime, protein motion is given by $\dot{\vec{X}} = \frac{1}{\gamma}\left(\vec{F}+\vec{R}\right)$. In the model, each circular domain has its own associated $\gamma$ factor given by Stokes' Law as $\gamma_i = 6\pi\nu R_i$ with dynamic viscosity $\nu$ \cite{stokeslaw}. The force on each domain is given by $\vec{F} = \vec{F}_{spr} + \vec{T}$, where $\vec{T}$ is the tension force between domains maintaining the rigid rod constraint. Each domain feels not only a harmonic restoring force, but also a Brownian force $\vec{R}$. This force is a Gaussian-distributed zero-mean magnitude with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ \cite{einstein} and uniformly random direction.

@@

>>>>

Dynein's mechanism of motion generation is the least understood of all motor proteins. Kinesin and myosin both take consistent steps of the same size \cite{kinesin-step-size, myosin-step-size}. In contrast, dynein is known to take highly variant steps both forwards and backwards, but averaging 16nm \cite{yildizpaper, weihongpaper}. Another interesting feature of dynein is the 20nm separation between its ATP hydrolysis and the site and MT binding site \cite{3vkh-cite}. The protein must transmit information about ATP binding across this distance in order to coordinate its steps \cite{mt-atp-coupling}. Explaining these phenomena is necessary to fully understand dynein's mechanism.\\

@@

\subsection*{Equilibrium forces}
The onebound model has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$. The bothbound model has two: $\theta_{nm}$ and $\theta_{fm}$. The model is free to vary across all of these degrees of freedom, barring steric interactions with the microtubule. These angles describe a planar model which is not capable of transverse motion. To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for onebound and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for bothbound. Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain. These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}. These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}. Electron microscopy studies using ADP-Vi to freeze dynein in the pre-powerstroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.\\

\subsection*{Brownian dynamics}
Brownian dynamics is used to study the model's dynamics in a biophysical manner. In the Brownian regime, protein motion is given by $\dot{\vec{X}} = \frac{1}{\gamma}\left(\vec{F}+\vec{R}\right)$. In the model, each circular domain has its own associated $\gamma$ factor given by Stokes' Law as $\gamma_i = 6\pi\nu R_i$ with dynamic viscosity $\nu$ \cite{stokeslaw}. The force on each domain is given by $\vec{F} = \vec{F}_{spr} + \vec{T}$, where $\vec{T}$ is the tension force between domains maintaining the rigid rod constraint. Each domain feels not only a harmonic restoring force, but also a Brownian force $\vec{R}$. This force is a Gaussian-distributed zero-mean magnitude with variance $R_{\sigma^2} = \sqrt{\frac{2k_bT\gamma}{\delta t}}$ and uniformly random direction.

@@

Describe fig:stroke results here.
The transition rate from pre->post powerstroke compares roughly with MD simulations of the powerstroke \cite{mdstroke}. - is this actually true?
